---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lin.Reg)
```

## Decription of `lin.Reg`
This is the function will you can perform univariate or multivariate linear regression models. A second function of `summary.lin.Reg` is also included for displaying the results of linear regression.

## Examples
### using for univariate
```{r uni}
set.seed(2021)
X = rnorm(100)
Y = X * 3 + rnorm(5)

model_uni = lin.Reg(Y,X)
```

Using `summary.lin.Reg` to display the result:
```{r}
summary.lin.Reg(model_uni)
```


### using for multivariates
```{r multi}
set.seed(2021)
X = matrix(rnorm(100), 50, 2)
Y = matrix((X[,1]+ 5*X[,2] + rnorm(50,sd=2)), 50, 1)

model_multi = lin.Reg(Y,X)
```

Using `summary.lin.Reg` to display the result:
```{r}
summary.lin.Reg(model_multi)
```

## Troubleshoot
In same cases, the function will not perform correctly, several error message will then show up

For example, if the response variable are provided more then 1 columns, which is not allowed in this model, a error message will show like this:
```{r error_mess}
set.seed(2021)
X = matrix(rnorm(50), 5, 2)
Y = matrix((X[,1]+ 5*X[,2] + rnorm(50,sd=2)), 100, 2)

try(lin.Reg(Y,X))
```


## Benchmark
### comparing with `lm()`
```{r benchmart}
X1 = rnorm(100)
X2 = rnorm(100)
X= cbind(X1,X2)

Y = X1+ 5*X2 + rnorm(100,sd=5)

benchmark <- bench::mark(lm(Y~X1+X2)$coefficients, 
                     lin.Reg(Y,X)$coefficients)
benchmark
```

Compare with the traditional linear regression model, the minimum and median bench time is much smaller, as well as the memory allocation needed.
















